EDA

### 2020-03-01 src/EDA&mode_fitting.Rmd
a few errors in lm model fixed

linear_full<-lm(rate~.,data=assessment_aggregate)
summary(linear_full)

library(broom)
linear_full_fit<-augment(linear_full)
sqrt(sum((linear_full_fit$.resid)^2)/nrow(assessment_aggregate)) #  2.772333

```
Multiple R-squared:  0.7803,	Adjusted R-squared:  0.7503 
MSPE = 2.772333

Next: variable selection
with only significant variables
```{r}
reduced<-lm(rate~Year+TaxClassCode+AddressAssessorMunicipalityDesc, data=assessment_aggregate)
summary(reduced)

reduced_fit<-augment(reduced)
sqrt(sum((reduced_fit$.resid)^2)/nrow(assessment_aggregate)) #  2.861619

```
Multiple R-squared:  0.7659,	Adjusted R-squared:  0.7408 
MSPE = 2.861619
With fewer variables, adjusted R-squared declines.

By comparing the two models, the fit of full model is better.

@@

Elastic net: 
reference: https://daviddalpiaz.github.io/r4sl/elastic-net.html
```{r}
library(caret)
tibble::as_tibble(assessment_aggregate)
cv_10 = trainControl(method = "cv", number = 10)
elastic_net = train(
  rate~., data = assessment_aggregate,
  method = "glmnet",
  trControl = cv_10
)
elastic_net
```
The final values used for the model were alpha = 0.1 and lambda = 0.09334029.
MSPE = 3.066083  
R squared = 0.7459584

@@

newx<-test[,-c(8)]
y<-test[,c(8)]
linear_1<-lm(rate ~.,data=train)
resid<-predict(linear_1,newdata = newx) - y
sqrt(sum(resid^2)/nrow(test))
```
MSPE = 3.52065

Reduced model
```{r}
# reduced variable
linear_2<-lm(rate~Year+TaxClassCode+AddressAssessorMunicipalityDesc,data=train)
resid<-predict(linear_2,newdata = newx) - y
sqrt(sum(resid^2)/nrow(test))
# 3.516749
```
MSPE = 3.516749

@@

Elastic Net
```{r}
tibble::as_tibble(assessment_aggregate[train_ind,])
cv_10 = trainControl(method = "cv", number = 10)
elastic_net = train(
  rate~., data = assessment_aggregate[train_ind,],
  method = "glmnet",
  trControl = cv_10
)
elastic_net
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were alpha = 0.55 and lambda = 0.009140377.

ridge_reg = glmnet(x_train, y_train, nlambda = 25, alpha = 0.55, family = 'gaussian', lambda = 0.009140377)
predictions_test <- predict(ridge_reg, newx = x_test)
eval_results(y_test, predictions_test)
```
MSPE = 2.566096

>>>>

colnames(assessment_aggregate)
linear_full<-lm(rate~factor(AddressAssessorMunicipalityDesc)+factor(Year)+factor(TaxClassCode)+assessTotal+landTotal+improvementTotal+propertyCount+predTaxIncome,data=assessment_aggregate)
summary(linear_full)

library(broom)
linear_full_fit<-augment(linear_full)
sqrt(sum((linear_full_fit$.resid)^2)/nrow(assessment_aggregate)) 
```
Multiple R-squared:  0.8874,	Adjusted R-squared:  0.8708 
MSPE = 1.984109

Next: variable selection
with only significant variables
```{r}
reduced<-lm(rate~factor(Year)+factor(TaxClassCode)+factor(AddressAssessorMunicipalityDesc), data=assessment_aggregate)
summary(reduced)

reduced_fit<-augment(reduced)
sqrt(sum((reduced_fit$.resid)^2)/nrow(assessment_aggregate))
```
Multiple R-squared:  0.8826,	Adjusted R-squared:  0.8679 
MSPE = 2.02679
With fewer variables, adjusted R-squared declines.

By comparing the two models, the fit of full model is the better of the two.

@@

Elastic net: 
reference: https://daviddalpiaz.github.io/r4sl/elastic-net.html
```{r}
library(caret)
tibble::as_tibble(assessment_aggregate)
cv_10 = trainControl(method = "cv", number = 10)
elastic_net = train(
  rate~factor(AddressAssessorMunicipalityDesc)+factor(Year)+factor(TaxClassCode)+assessTotal+landTotal+improvementTotal+propertyCount+predTaxIncome, data = assessment_aggregate,
  method = "glmnet",
  trControl = cv_10
)
elastic_net
```
The final values used for the model were alpha = 0.1 and lambda = 0.007102922.
 alpha  lambda       RMSE      Rsquared   MAE     
  0.10   0.007102922  2.238720  0.8623328  1.711568

@@

newx<-test[,-c(8)]
y<-test[,c(8)]
linear_1<-lm(rate~factor(AddressAssessorMunicipalityDesc)+factor(Year)+factor(TaxClassCode)+assessTotal+landTotal+improvementTotal+propertyCount+predTaxIncome,data=train)
resid<-predict(linear_1,newdata = newx) - y
sqrt(sum(resid^2)/nrow(test))
```
MSPE =  2.592136

Reduced model
```{r}
# reduced variable
linear_2<-lm(rate~factor(Year)+factor(TaxClassCode)+factor(AddressAssessorMunicipalityDesc),data=train)
resid<-predict(linear_2,newdata = newx) - y
sqrt(sum(resid^2)/nrow(test))
```
MSPE = 2.537555

@@

Elastic Net
```{r}
tibble::as_tibble(assessment_aggregate[train_ind,])
cv_10 = trainControl(method = "cv", number = 10)
elastic_net = train(
 rate~factor(AddressAssessorMunicipalityDesc)+factor(Year)+factor(TaxClassCode)+assessTotal+landTotal+improvementTotal+propertyCount+predTaxIncome, 
 data = assessment_aggregate[train_ind,],
  method = "glmnet",
  trControl = cv_10
)
elastic_net

# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were alpha = 1 and lambda = 0.006549203.

elastic_reg = glmnet(x_train, y_train, nlambda = 25, alpha = 1, family = 'gaussian', lambda =  0.006549203)
predictions_test <- predict(elastic_reg, newx = x_test)
eval_results(y_test, predictions_test)
```
MSPE = 2.559923
